
\runninghead{Johnston, Milthorpe}
\title{Benchmarking bioinformatics workloads and exploring suitability for heterogeneous HPC}
\author{Beau Johnston and Josh Milthorpe\affilnum{1}}

\affiliation{\affilnum{1}The Australian National University, AU}
\corrauth{Beau Johnston,
    Research School of Computer Science,
    The Australian National University,
    Canberra, ACT, AU.}
\email{beau.johnston@anu.edu.au}

\begin{abstract}
For reasons of both performance and energy efficiency, high-performance computing (HPC) hardware is becoming increasingly heterogeneous.
The OpenCL framework supports portable programming across a wide range of computing devices and is gaining influence in programming next-generation accelerators.
To characterize the performance of these devices across a range of applications requires a diverse, portable and configurable benchmark suite, and OpenCL is an attractive programming model for this purpose.

We present an extended and enhanced version of the OpenDwarfs OpenCL benchmark suite, with a strong focus placed on the robustness of applications, curation of additional benchmarks with an increased emphasis on correctness of results and choice of problem size.
Preliminary results and analysis are reported for eight benchmark codes on a diverse set of architectures -- three Intel CPUs, five Nvidia GPUs, six AMD GPUs and a Xeon Phi.

Additionally, we examine the architecture-independent characteristics of a subset of bioinformatics codes from OpenDwarfs.
This is performed to gain insights around the suitability of heterogeneous computing nodes for bioinfomatics workloads, and shows the best and worst characteristics of these codes when using accelerators.
\end{abstract}

\keywords{workload characterization, benchmarking, bioinformatics, accelerators, heterogeneous HPC}

\maketitle
